
---
title: "Exponential Smoothing Forecasting"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
   

---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

```{r xaringan-tile-view, echo=FALSE}
xaringanExtra::use_tile_view()
```


```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

```{r, echo=FALSE}
xaringanExtra::use_webcam()
```

```{r xaringan-fit-screen, echo=FALSE}
xaringanExtra::use_fit_screen()
```

### Forecasting with Exponential Smoothing

- Single ES: constant level (no trend) and no seasonality

- Holt’s Exponential Smoothing (Using double ES): has trend and no seasonality. 

- Holt-Winters Exponential Smoothing (Using triple ES): has trend and seasonality. 

---
class: inverse, center, middle

# Forecasting with Single Exponential Smoothing

- constant level (no trend) and no seasonality

---
### Forecasting with Single Exponential Smoothing

```{r, eval=FALSE}
library(forecast)
rain <- read.csv('rainfall_london.csv')
ts1 <- ts(rain,start=c(1813))
plot(ts1)
```




---
### Forecasting with Single Exponential Smoothing

```{r, echo=FALSE}
library(forecast)
rain <- read.csv('rainfall_london.csv')
ts1 <- ts(rain,start=c(1813))
plot(ts1)
```


---
### Making Forecast

```{r}
ts1_forecast <- HoltWinters(ts1, alpha=TRUE, 
                            beta=FALSE, 
                            gamma=FALSE)
ts1_forecast
```

---

```{r}
plot(ts1_forecast)
```

---
### Forecasting

```{r}
ts1_forecast2 <- forecast(ts1_forecast, h=8)
ts1_forecast2
```

---
```{r}
plot(ts1_forecast2)
```


---
class: center, middle, inverse

### Holt’s Exponential Smoothing

- Increasing or decreasing trend and no seasonality

---
**Holt’s Exponential Smoothing**

```{r}
skirts <- read.csv('skirts.csv')
ts2 <- ts(skirts,start=c(1866))
plot(ts2)
```

---

```{r}
ts2_forecast <- HoltWinters(ts2, alpha=TRUE, 
                            beta=TRUE, 
                            gamma=FALSE)
ts2_forecast
```

---

```{r}
plot(ts2_forecast)
```

---

```{r}
ts2_forecast2 <- forecast(ts2_forecast, h=19)
plot(ts2_forecast2)
```

---
class: center, inverse, middle
### Holt-Winters Exponential Smoothing

-  increasing or decreasing trend and seasonality. 

---
```{r}
souvenir <- read.csv('souvenir.csv')
ts3 <- ts(souvenir, frequency=12, start=c(1987,1))
plot(ts3)
```


---
```{r}
ts3_forecasts <- HoltWinters(ts3, alpha=TRUE, 
                            beta=TRUE, 
                            gamma=TRUE)
plot(ts3_forecasts)
```


---
```{r}
ts3_forecasts2 <- forecast(ts3_forecasts, h=48)
plot(ts3_forecasts2)
```


---

```{r, eval=FALSE}
souvenir <- read.csv('souvenir.csv')
ts3 <- ts(souvenir, frequency=12, start=c(1987,1))
logts3 <- log(ts3)
ts3_forecasts <- HoltWinters(logts3)
plot(ts3_forecasts)
ts3_forecasts2 <- forecast(ts3_forecasts, h=48)
plot(ts3_forecasts2)
```


---

- The parameters alpha, beta and gamma all have values between 0 and 1.

- Values that are close to 0 mean that relatively little weight is placed on the most recent observations (the weights are spread out for the past observations) when making forecasts of future values.

- Alpha estimates the level

- Beta estimate the slopes of the trend component

- Gamma estimate the slope of the seasonal component