---
title: "Exponential Smoothing Forecasting"
format: 
  beamer
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

# Forecasting with Exponential Smoothing

- Single ES: constant level (no trend) and no seasonality

- Holt’s Exponential Smoothing (Using double ES): increasing or decreasing trend and no seasonality. 

- Holt-Winters Exponential Smoothing (Using triple ES): increasing or decreasing trend and seasonality. Holt and Winter 

# Forecasting with Single Exponential Smoothing

```{r, echo=FALSE}
library(forecast)
rain <- read.csv('rainfall_london.csv')
ts1 <- ts(rain,start=c(1813))
plot(ts1)
```


# Making Forecast

```{r}
ts1_forecast <- HoltWinters(ts1, beta=FALSE, gamma=FALSE)
ts1_forecast
```

#

```{r}
ts1_forecast$fitted
plot(ts1_forecast)
```

# Forecasting

```{r}
ts1_forecast2 <- forecast(ts1_forecast, h=8)
ts1_forecast2
plot(ts1_forecast2)
```

# Holt’s Exponential Smoothing

- Increasing or decreasing trend and no seasonality

```{r}
skirts <- read.csv('skirts.csv')
ts2 <- ts(skirts,start=c(1866))
plot(ts2)
```

# 

```{r}
ts2_forecast <- HoltWinters(ts2, gamma=FALSE)
ts2_forecast
plot(ts2_forecast)
ts2_forecast2 <- forecast(ts2_forecast, h=19)
plot(ts2_forecast2)
```


# Holt-Winters Exponential Smoothing

- increasing or decreasing trend and seasonality

```{r}
souvenir <- read.csv('souvenir.csv')
souvenirtimeseries <- ts(souvenir, frequency=12, start=c(1987,1))
logsouvenirtimeseries <- log(souvenirtimeseries)
souvenirtimeseriesforecasts <- HoltWinters(logsouvenirtimeseries)
plot(souvenirtimeseriesforecasts)
```

#

```{r}
souvenirtimeseriesforecasts2 <- forecast(souvenirtimeseriesforecasts, h=48)
plot(souvenirtimeseriesforecasts2)
```

#

```{r}
souvenir <- read.csv('souvenir.csv')
souvenirtimeseries <- ts(souvenir, frequency=12, start=c(1987,1))
logsouvenirtimeseries <- souvenirtimeseries
souvenirtimeseriesforecasts <- HoltWinters(logsouvenirtimeseries)
plot(souvenirtimeseriesforecasts)
souvenirtimeseriesforecasts2 <- forecast(souvenirtimeseriesforecasts, h=48)
plot(souvenirtimeseriesforecasts2)
```


#

- The parameters alpha, beta and gamma all have values between 0 and 1.

- Values that are close to 0 mean that relatively little weight is placed on the most recent observations (the weights are spread out for the past observations) when making forecasts of future values.

- Alpha estimates the level

- Beta estimate the slopes of the trend component

- Gamma estimate the slope of the seasonal component