---
title: "An Overview of Data Mining"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
   

---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-tile-view, echo=FALSE}
xaringanExtra::use_tile_view()
```


```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

```{r, echo=FALSE}
xaringanExtra::use_webcam()
```

```{r xaringan-fit-screen, echo=FALSE}
xaringanExtra::use_fit_screen()
```


--- 
#  Cross Sectional vs. Time Series

-   Cross Sectional Data: Multiple objects observed at a particular point of time

--- 
#  Cross Sectional vs. Time Series

- Cross Sectional Data: Multiple objects observed at a particular point of time

- Examples: customers’ behavioral data at today’s update, companies’ account balances
at the end of the last year, patients’ medical records at the end of the current month.

--- 
#  Cross Sectional vs. Time Series

- Cross Sectional Data: Multiple objects observed at a particular point of time

- Examples: customers’ behavioral data at today’s update, companies’ account balances
at the end of the last year, patients’ medical records at the end of the current month.

- Time Series Data: One single object (product, country, sensor, ..) observed over multiple equally-spaced
time periods

--- 
#  Cross Sectional vs. Time Series

- Cross Sectional Data: Multiple objects observed at a particular point of time

- Examples: customers’ behavioral data at today’s update, companies’ account balances
at the end of the last year, patients’ medical records at the end of the current month.

- Time Series Data: One single object (product, country, sensor, ..) observed over multiple equally-spaced
time periods

 - Examples: quarterly Italian GDP of the last 10 years, weekly supermarket sales of the
previous year, yesterday’s hourly temperature measurements. 


--- 
#  

```{r}
#  define data
library(ggfortify)
library(tidyverse)
library(xts)
library(fpp2)
library(TTR)
sales=BJsales
earnings=JohnsonJohnson
nile=Nile
url="http://www.cru.uea.ac.uk/cru/data/temperature/CRUTEM3v-gl.dat"
f=read.table(url,fill=TRUE)
ny=nrow(f)/2;x=c(t(f[2*1:ny-1,2:13]))
temperature=ts(x,start=2019,frequency=12,end=c(2020,1))
autoplot(temperature)+ ggtitle("World Temperature")
```

--- 
#  

```{=tex}
\begin{center}
\Huge Smoothing
\end{center}
```

--- 
#  6. Smoothing

-   Smoothing is usually done to reveal the series patterns and trends.

--- 
#  Simple Moving Average Smoothing

-   Moving Average (MA) creates a new series by averaging the most recent observations from the original series.

-   MA(k) creates $s_t$ as follows.

$$
s_{t} = \frac{y_t + y_{t-1} +...+ y_{t-k+1}}{k}
$$

-   Larger $k$ will smooth the series more strongly

--- 
#  

```{r}
d <- read_csv('data/MedCPISmooth.csv')
t1 = ts(d$PerMEDCPI, start = c(1947, 1), frequency = 4)
k = 8
t1_sma = SMA(t1, n = k)
plot(t1, main = paste0("Medical Component of the CPI"))
```

--- 
#  

```{r}
d <- read_csv('data/MedCPISmooth.csv')
t1 = ts(d$PerMEDCPI, start = c(1947, 1), frequency = 4)
k = 4
t1_sma = SMA(t1, n = k)
plot(t1, main = paste0("Moving average with k = ",k))
lines(t1_sma, col = "red")
```

--- 
#  

```{r}
d <- read_csv('data/MedCPISmooth.csv')
t1 = ts(d$PerMEDCPI, start = c(1947, 1), frequency = 4)
k = 8
t1_sma = SMA(t1, n = k)
plot(t1, main = paste0("Moving average with k = ",k))
lines(t1_sma, col = "red")
```

--- 
#  

```{r}
d <- read_csv('data/MedCPISmooth.csv')
t1 = ts(d$PerMEDCPI, start = c(1947, 1), frequency = 4)
k = 16
t1_sma = SMA(t1, n = k)
plot(t1, main = paste0("Moving average with k = ",k))
lines(t1_sma, col = "red")
```

--- 
#  

```{r}
#  Data 1
t1 = read_csv("beer.csv")
t1 = ts(t1, start = c(1956, 1), freq = 4)
k = 1
t1_sma = SMA(t1, n = k)
plot(t1, main = paste0("Original Series"))
```

--- 
#  

```{r}
t1 = read_csv("beer.csv")
t1 = ts(t1, start = c(1956, 1), freq = 4)
k = 2
t1_sma = SMA(t1, n = k)
plot(t1, main = paste0("Moving average with k = ",k))
lines(t1_sma, col = "red")
```

--- 
#  

```{r}
k = 5
t1_sma = SMA(t1, n = k)
plot(t1, main = paste0("Moving average with k = ",k))
lines(t1_sma, col = "red")
```

--- 
#  

```{r}
k = 12
t1_sma = SMA(t1, n = k)
plot(t1, main = paste0("Moving average with k = ",k))
lines(t1_sma, col = "red")
```

--- 
#  Forecasting

-   We can use smoothing for forecasting

-   We have \begin{align*}
    \hat{s}_t &= \frac{y_t + y_{t-1} +...+ y_{t-k+1}}{k}\\
    &=\frac{y_t + y_{t-1} +...+ y_{t-k+1}+y_{t-k}-y_{t-k}}{k}\\
    &=\frac{y_t + \bigg(y_{t-1} +...+ y_{t-k+1}+y_{t-k}\bigg)-y_{t-k}}{k}\\
    &= \frac{y_t + k\hat{s}_{t-1}-y_{t-k}}{k}\\
    &= \hat{s}_{t-1} + \frac{y_t-y_{t-k}}{k}
    \end{align*}

--- 
#  Forecasting

-   If there is no trend in $y_t$ the second term $(y_t-y_{t-k})/k$ can be ignored
-   Forecasting $l$ lead time into future by

$$
\hat{y}_{T+l} = \hat{s}_T
$$

-   If there is a linear trend in a series, we can use the double moving average to estimate the trend (slope)

--- 
#  

```{=tex}
\begin{center}
\Huge Double MA
\end{center}
```
--- 
#  7. Double MA

-   Linear trend time series: $$
    y_t = \beta_0 + \beta_1t +\epsilon_t
    $$

-   Step 1: Smooth the series $$
    \hat{s}^{(1)}_{t} = \frac{y_t + y_{t-1} +...+ y_{t-k+1}}{k}
    $$

-   Step 2: Smooth the smoothed series $$
    \hat{s}^{(2)}_{t} = \frac{\hat{s}^{(1)}_t + \hat{s}^{(1)}_{t-1} +...+ \hat{s}^{(1)}_{t-k+1}}{k}
    $$

-   Step 3: Calculate the trend $$
    b_1 = \hat{\beta_1} =  \frac{2}{k-1}\bigg(\hat{s}_T^{(1)}-\hat{s}_T^{(2)}\bigg)
    $$

--- 
#  Forecasting

-   Forecasting $l$ lead time into future by $$
    \hat{y}_{T+l} = \hat{s}_T + b_1 \cdot l
    $$

--- 
#  

You are given the following time series

| $t$   | 1   | 2   | 3   | 4   | 5   |
|:------|:----|:----|:----|:----|:----|
| $y_t$ | 1   | 3   | 5   | 8   | 13  |

-   Forecasting $y_{7}$ using simple moving average with $k = 2$

-   Forecasting $y_{7}$ using double moving average with $k = 2$

--- 
#  

--- 
#  Example

-   We simulate 100 data points ($T=100$) of $$
    y_t = 1 +3t + \epsilon, 
    $$ where, $\epsilon \sim N(0, 5^2)$.

--- 
#  

```{r}
set.seed(2022)
n = 100
y = rep(0, n)

y[1] = 0
b0 = 1
b1 = 3

e = rnorm(n, sd = 5)

for (t in 2:n)
{
  y[t] = b0 + b1*t+e[t]
}

k = 12 
s1 = SMA(y, n = k)
s2 = SMA(s1, n = k)


b1_hat = 2*(s1[n]-s2[n])/(k-1)

autoplot(ts(y)) + ggtitle("Original Series")
```

--- 
#  

```{r}
autoplot(ts(s1)) + ggtitle(paste0("MA Series with k = ",k))
```

--- 
#  

```{r}
autoplot(ts(s2)) + ggtitle(paste0("Double MA Series with k = ",k))
```

--- 
#  

-   Using the above steps, the estimated trend is $b_1 = 2.92$

-   The forecast for the next points from $y_{100}$ is

$$
    \hat{y}_{100+l} = \hat{s}_{100}+ b_1\cdot l = \hat{s}_{100}+ 2.92\cdot l
$$

--- 
#  

```{=tex}
\begin{center}
\Huge Exponential Smoothing
\end{center}
```
--- 
#  Exponential Smoothing

-   MA distributes the weight equally to the recent observations

-   Exponential Smoothing controls the weights of the recent observations by $w$

$$
\hat{s}_{t} = \frac{y_t + wy_{t-1} + w^2y_{t-2} + ... + w^ty_0}{1/(1-w)}
$$

-   Smaller $w$ ($w \to 0$) gives higher weights to the more recent observations

-   Smaller $w$ smooths the series more lightly.

--- 
#  Exponential Smoothing

-   We have \begin{align*}
    \hat{s}_{t} &= \hat{s}_{t-1} + (1-w)(y_t-\hat{s}_{t-1})\\
    & = (1-w)y_t + w\hat{s}_{t-1}
    \end{align*}

-   When $w \to 0$, $\hat{s}_{t} \to y_t$, or little smoothing has taken

--- 
#  

```{r}
#  In exponential smoothing, a higher ratio will weight more on the recent observation, 
#  ratio close to 1 will have a 100% weight on the most recent observation
alpha = .9
t1_ema = EMA(t1, ratio = alpha)
plot(t1,  main = paste0("Exponential Smoothing with w = ", 1- alpha))
lines(t1_ema, col = "red")
```

--- 
#  

```{r}
#  In exponential smoothing, a higher ratio will weight more on the recent observation, 
#  ratio close to 1 will have a 100% weight on the most recent observation
alpha = .5
t1_ema = EMA(t1, ratio = alpha)
plot(t1,  main = paste0("Exponential Smoothing with w = ", 1- alpha))
lines(t1_ema, col = "red")
```

--- 
#  

```{r}
#  In exponential smoothing, a higher ratio will weight more on the recent observation, 
#  ratio close to 1 will have a 100% weight on the most recent observation
alpha = .1
t1_ema = EMA(t1, ratio = alpha)
plot(t1,  main = paste0("Exponential Smoothing with w = ", 1- alpha))
lines(t1_ema, col = "red")
```

--- 
#  

```{=tex}
\begin{center}
\Huge Double Exponential Smoothing
\end{center}
```
--- 
#  Double Exponential Smoothing

We can use double smoothing to identify the trend and forecast linear trend time series as follows.

-   Step 1: Create a smoothed series: $\hat{s}^{(1)}_{t} = (1-w)y_t + w\hat{s}^{(1)}_{t-1}$

-   Step 2: Create a double smoothed series: $\hat{s}^{(2)}_{t} = (1-w)\hat{s}^{(1)}_{t} + w\hat{s}^{(2)}_{t-1}$

-   Step 3: Estimate the trend: $$
    b_1 = \frac{1-w}{w}(\hat{s}^{(1)}_{T}-\hat{s}^{(2)}_{T})
    $$

-   Step 4: Forecast

$$
\hat{y}_{T+l} = 2\hat{s}^{(1)}_{T}-\hat{s}^{(2)}_{T}+b_1\cdot l
$$

--- 
#  Example

You are given the following time series

| $t$   | 1   | 2   | 3   | 4   | 5   |
|:------|:----|:----|:----|:----|:----|
| $y_t$ | 1   | 3   | 5   | 8   | 13  |

-   Forecasting $y_{7}$ using exponential smoothing with $w = .8$

-   Forecasting $y_{7}$ using double exponential smoothing with $w = .8$
