
---
title: "Analyzing frequency: tf-idf"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      
   

---
class: inverse, middle, center

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
```

---
Suppose we have a text data that contains $n$ document as below. 

| Document  |   Texts         |
|---|------------|
| 1  | blah blah  | 
| 2  |  blah blah |
| ...  | ...        |
| n  | blah blah   | 

- A document could be a sentence, a paragraph 

- A document contains of `terms`.  Terms could be a word or a collection of words

- How important is a word/term to a document?

---
# Term frequency (tf)

- The more often the words show up the more important it is

- We could use `Term Frequency`   

- TF (Term Frequency) = (Number of times term `t` appears in a document) / (Total number of terms in the document).

- Please notice that the same word/term may have different `tf` in a different document

- For example: the word `love` in document 1 may have different `tf` when compared with that of document 2. 

---
# Example

- Calculate the term frequency of the word `cats` for each document in the below text dataset. 


|   | Document     |
|:---|:--------------|
| 1 | I love cats. Cats are renowned for their graceful agility. Cats are awesome!  |
| 2 | Cats are furry animals that like to sleep.            |
| 3 | Dogs and cats are popular pets that bring joy to many families            |
| 4 | Dogs are friendly animals that enjoy companionship.            |

---
# Issues with Term frequency (tf)

- Sometimes: Rare terms are more informative than frequent terms

    - Example: “the”, “is”, “of”...

- We should remove some words such as “the”, “is”, “of” if we use `tf` as a measure of importance

- Or we could create a `weight` for a term so that the rare words would have higher weights.

- Inverse Document Frequency (idf) is such a weight


---
# Inverse Document Frequency (idf)

- IDF (Inverse Document Frequency) = log_e(Total number of documents / Number of documents with term `t` in it).

$$idf(t) = \ln \bigg(\frac{\text{Total number of documents}}{\text{Number of documents with term t in it}} \bigg)$$

- The idf of a rare term is high, whereas the idf of a frequent term is likely to be low

- The `idf` of a term is a constant throughout the document.  For example the word `love` in Document 1 should have the same `idf` as the word `love` in Document 2. 

---
# tf-idf


$$\text{tf-idf }(t) = \text{tf }(t) \cdot \text{tf }(t) $$

- The `tf-idf` of the same term may have different values in different documents.  For example the word `love` in Document 1 may have a different value `tf-idf` compared to the word `love` in Document 2. 


---
# Example

- Calculate the idf and tf-idf of the word `cats` for the documents in the below text dataset. 


|   | Document     |
|:---|:--------------|
| 1 | I love pets. Cats are renowned for their graceful agility. Cats are awesome!  |
| 2 | Cats are friendly animals that like to sleep.            |
| 3 | Dogs and cats are friendly pets that bring joy to many families            |
| 4 | Dogs are friendly animals that enjoy companionship.            |

---
# Example

[Sample Codes](assignment14_codes.html)

```{r}
library(tidyverse)
library(ggplot2)
library(tidytext)
df <- read_csv('amazon_reviews.csv')

df = df %>% 
  select(name, reviews.text) %>% 
  filter(name %in% c('Amazon Kindle Paperwhite - eBook reader - 4 GB - 6 monochrome Paperwhite - touchscreen - Wi-Fi - black,,,',	
'All-New Fire HD 8 Tablet, 8 HD Display, Wi-Fi, 16 GB - Includes Special Offers, Magenta')) %>% 
  rename(texts = reviews.text,
         document = name)


stop_word2 = tibble(word = c(letters, LETTERS, "oh", 'just'))

df_words = df %>% 
  unnest_tokens(input = texts, output = word) %>% 
  count(document, word, sort = TRUE) %>% 
  anti_join(get_stopwords()) %>% 
  anti_join(stop_word2)

total_words <- df_words %>% 
  group_by(document) %>% 
  summarize(total = sum(n))

df_words <- left_join(df_words, total_words)

df_tf = df_words %>% 
  group_by(document) %>% 
  mutate(tf = n/total)

df_tf %>% 
  group_by(document) %>% 
  slice_max(tf, n = 5) %>% 
  ungroup() %>%
  ggplot(aes(tf, fct_reorder(word, tf), fill = document)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~document, ncol = 2, scales = "free") +
  labs(x = "tf", y = NULL)


```

---
# Plot tf-idf

```{r}
df_tf_idf <- df_words %>%
  bind_tf_idf(word, document, n)

library(forcats)
df_tf_idf %>%
  group_by(document) %>%
  slice_max(tf_idf, n = 15) %>%
  ungroup() %>%
  ggplot(aes(tf_idf, fct_reorder(word, tf_idf), fill = document)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~document, ncol = 2, scales = "free") +
  labs(x = "tf-idf", y = NULL)

```




---

```{r, eval=FALSE, echo=FALSE}
library(tidyverse)
library(tidytext)
library(knitr)
library(kableExtra)
df <- read_csv('netflix_titles.csv')

df = df %>% 
  select(type, description) %>% 
  rename(texts = description,
         document = type)


df_words = df %>% 
  unnest_tokens(input = texts, output = word) %>% 
  anti_join(get_stopwords()) %>% 
  anti_join(tibble(word = c(letters, LETTERS, "oh", 'just'))) %>% 
  count(document, word, sort = TRUE)

total_words <- df_words %>% 
  group_by(document) %>% 
  summarize(total = sum(n))

df_words <- left_join(df_words, total_words)

df_tf = df_words %>% 
  group_by(document) %>% 
  mutate(tf = n/total)


df_tf %>% 
  group_by(document) %>% 
  slice_max(tf, n = 5) %>% 
  ungroup() %>%
  ggplot(aes(tf, fct_reorder(word, tf), fill = document)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~document, ncol = 2, scales = "free") +
  labs(x = "tf", y = NULL)


df_tf_idf <- df_words %>%
  bind_tf_idf(word, document, n)

library(forcats)

df_tf_idf %>%
  group_by(document) %>%
  slice_max(tf_idf, n = 15) %>%
  ungroup() %>%
  ggplot(aes(tf_idf, fct_reorder(word, tf_idf), fill = document)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~document, ncol = 2, scales = "free") +
  labs(x = "tf-idf", y = NULL)
```














