---
title: "Assignment 15 - tf-idf"
format: 
  html: 
    toc: true
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

------------------------------------------------------------------------

### Instruction

*Write your codes in Rmarkdown or Quarto then knit it to a Word or pdf document. Submit the Word document*

------------------------------------------------------------------------

### Question 1. 

Given the following text dataset. **Calculate by hand** for this question. 

| document   | texts      |
|:---|:--------------|
| 1 | I love pets. Cats are renowned for their graceful agility. Cats are awesome!  |
| 2 | Cats are friendly animals that like to sleep. Which one is more friendly?             |
| 3 | Dogs and cats are friendly pets that bring joy to many families            |
| 4 | Dogs are friendly animals that enjoy companionship. Friendly! Friendly!            |

1. Calculate the term frequency (tf) of the term `animals` for each document

2. Calculate the `idf` the term `animals`

3. Calculate the `tf-idf` of the term `animals` for each document.

4. Redo 1-3 with the term `friendly`.   


### Question 2.  

Reproduce the results the codes in the sample codes

[Sample Codes](assignment14_codes.html)


### Question 3.

Redo the sample codes with differenct selections of documents

### Question 4.  

Working with the Netflix dataset containing descriptions of movies and TV shows on Netflix.

[Dataset](netflix_titles.csv)

Do the follows.

- Define your own documents for the analysis.

- Plot the  term frequency in the documents

- Plot the tf-idf in the documents. 

You can find sample codes for this question at

[Sample Codes](assignment14_codes.html)

```{r, echo=FALSE, eval=FALSE}
library(tidyverse)
library(tidytext)
library(knitr)
library(kableExtra)
df <- read_csv('netflix_titles.csv')

df = df %>% 
  select(title, description) %>% 
  filter(title %in% titles)

```

### Question 5. 

Redo Question 4 on your own dataset. 
