---
title: "Assignment 2: Exponential Smoothing"
format: html
editor: visual
---

------------------------------------------------------------------------

***Submission***: Submit photos of the answers to Canvas. For Question 3, submit the plot of the R-code to Canvas.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

------------------------------------------------------------------------

**Question 1.** *Calculation*

Given the following time series $y_t$.

| t   | $y_t$ |
|:----|:------|
| 1   | 1     |
| 2   | 3     |
| 3   | 5     |
| 4   | 8     |
| 5   | 12    |

a.  Calculate the exponential smoothing series with $w = .2$

b.  Calculate the double exponential smoothing series with $w = .2$

```{r, eval=FALSE, echo=FALSE}

y = c(1, 3, 5, 8, 12)
expo = function(y, w)
{
  s = y
  
  for (i in c(2:length(y)))
  {
    s[i] = (1-w)*y[i] + w*s[i-1]
  }

  return(s)  
}
```


**Question 2.** *Forecasting Linear Trend Time Series*

We assume the series in question 1 has linear trend. Use double exponential smoothing to estimate the linear trend (slope) of the time series. Use the estimated linear trend to predict the next value ($y_8$)

```{r, eval=FALSE, echo=FALSE}
s1 = expo(y, .2)
s2 = expo(s1, .2)

T = length(s1)

b1 = ((1-w)/w)*(s1[T]-s2[T])

l = 3
y[T+l] = s1[T]+b1*l

```

[SOLUTION](assignment2_sample.pdf)


------------------------------------------------------------------------
