---
title: "Assignment 2: Exponential Smoothing"
format: html
editor: visual
---

------------------------------------------------------------------------

***Submission***: Submit photos of the answers to Canvas. For Question 3, submit the plot of the R-code to Canvas.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

------------------------------------------------------------------------

For Question 1 and 2, a sample solution can be found at [Assignment 2's Sample](assignment2_sample.html)

**Question 1.** *Calculation*

Given the following time series $y_t$.

| t   | $y_t$ |
|:----|:------|
| 1   | 1     |
| 2   | 3     |
| 3   | 5     |
| 4   | 8     |
| 5   | 12    |
| 6   | 13    |
| 7   | 16    |

a.  Calculate the exponential smoothing series with $w = .2$

b.  Calculate the double exponential smoothing series with $w = .2$

**Question 2.** *Forecasting Linear Trend Time Series*

We assume the series in question 1 has linear trend. Use double exponential smoothing to estimate the linear trend (slope) of the time series. Use the estimated linear trend to predict the next value ($y_8$)

**Question 3.** *Trend Revealing by Visualization*

In this question, we will use R to plot a time series, create an MA series and plot the MA series.

-   Open Rstudio and use the following code to plot a time series.

```{r, eval=FALSE}
library(TTR)
# read data
d <- read.csv('https://bryantstats.github.io/math475/data/MedCPISmooth.csv')

# frequency = 4 for quarterly data, 
# frequency = 12 for monthly data, 
# frequency = 1 for yearly data, by default frequency = 1

t1 = ts(d$PerMEDCPI, start = 1947, frequency = 4)

# plot the time series
plot(t1, main = paste0("Medical Component of the CPI"))
```

-   Use the below codes to add an exponential smoothing series

```{r, eval=FALSE}
# In exponential smoothing, a higher ratio will weight more on the recent observation, 
# ratio close to 1 will have a 100% weight on the most recent observation
w = .1

t1_ema = EMA(t1, ratio = 1-w)

plot(t1,  main = paste0("Exponential Smoothing with w = ", w))
lines(t1_ema, col = "red")
```

-   Increase the value of $w$ to see the effect this parameter on the smoothing series. You can copy and paste the given codes and change the value of $w$.

**Question 4.** *Trend Revealing by Visualization*

In this assignment we will study the dataset about the economy of Algeria. The dataset can be download at [this link](data/algeria_economy.csv).

Use the sample codes in Question 3 to do the follows. Ask the instructor for any help.

-   Plot the time series of Algeria's Exports

-   Plot an exponential smoothing series for the above time series. What is your choice for $w$?

```{r, eval=FALSE, echo=FALSE}

d =  read.csv('data/algeria_economy.csv')
t2 = ts(d$Exports, start = 1960, frequency = 1)
w = .7

t2_ema = EMA(t2, ratio = 1-w)

plot(t2,  main = paste0("Exponential Smoothing with w = ", w))
lines(t2_ema, col = "red")
```

------------------------------------------------------------------------
