---
title: "Assignment 3: Time Series Decomposition"
format: html
editor: visual
---

------------------------------------------------------------------------

***Submission***: Submit photos of the answers to Canvas. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

------------------------------------------------------------------------

**Question** 

- Use the following codes to plot the Airline Passenger data and its additive decomposition

```{r, eval=FALSE}
data("AirPassengers")
plot(AirPassengers)
ourDecomposition <- decompose(AirPassengers, type="additive")
plot(ourDecomposition)
```

- Change `additive` to `multiplicative` to plot the multiplicative decomposition

- Plot the [Electric_Production](data/Electric_Production.csv) and its decomposition (*Notice: You need to use function `ts` to create the time series first*)

- Plot the [Electric_Production](data/Electric_Production.csv) from 1985 to 1995 and its decomposition

```{r, eval=FALSE, echo=FALSE}
d =  read.csv('data/Electric_Production.csv')
t2 = ts(d$IPG2211A2N, start = 1985, end = 1995, frequency = 12)
ourDecomposition <- decompose(t2, type="additive")
plot(ourDecomposition)
```

- (Ask the instructor:) Include your codes in an Rmarkdown or Quarto, Knit it to either pdf or Word document. Submit the file to Canvas.  
